---
title: "Text Mining and World Cloud "
output: html_notebook
---


```{r}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
```


```{r} 
#When wanting to load a file 
text <- readLines(file.choose())
```

```{r}
filePath <- "http://www.sthda.com/sthda/RDoc/example-files/martin-luther-king-i-have-a-dream-speech.txt"
filePath <- "~/Dropbox/R/TidyTextMining/1Peter"
text <- readLines(filePath)
docs <- Corpus(VectorSource(text))
inspect(docs)
```


### Text transformation 

We use the tm_map() function to replace the special characters and probably could be written simpler using the tidytext package 
```{r}
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")
```


### Cleaning Text 
```{r}
# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))

# Remove numbers
docs <- tm_map(docs, removeNumbers)

# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))

# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("blabla1", "blabla2")) 

# Remove punctuations
docs <- tm_map(docs, removePunctuation)

# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)

# Text stemming
# docs <- tm_map(docs, stemDocument)
```


### Term-Document Matrix 
```{r}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)
```


```{r}

X <- m #word frequency matrix
Y <- X >= 1
Y <- apply(Y, 2, as, "numeric") #boolean matrix
rownames(Y) <- rownames(X)
Z <- t(Y) %*% Y  #adjacency matrix
```


### Generating a Word Cloud
* words: the words to be ploted
* freq: their frequencies
* min.freq: Words with frequency below min.freq will not be plotted
* max.words: maximum number of words to be plotted
* random.order: plot words in random order. If false, they will be plotted in decreasing frequency 
* rot.per: proportion words with 90 degree rotation 
* colors: color words from least to most frequent 


```{r}
## will not be great here in the 
set.seed(1234)
  wordcloud(words = d$word, freq = d$freq, min.freq = 5,
          max.words=30, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```



```{r}
barplot(d[1:20,]$freq, las = 2, names.arg = d[1:20,]$word,
        col ="blue", main ="Most frequent words",
        ylab = "Word frequencies")
```



